\documentclass{sig-alternate-10pt}
\usepackage{url}
\usepackage[backgroundcolor=yellow]{todonotes}
% todonotes: \listoftodos & \todo{Some note or other.} & \missingfigure{}.
% todonotes: Options: 'disable' to not show these todo
\presetkeys{todonotes}{inline}{}

% Set letter paper size:
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\usepackage[
  pass,% keep layout unchanged
    % showframe,% show the layout
]{geometry}

\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

\tikzset{
      font={\fontsize{9pt}{10}\selectfont}}

\usepackage[font=footnotesize,labelfont=bf]{caption}

\begin{document}

\title{TCPSnitch: Dissecting the Usage of the Socket API}
%\titlenote{Produces the permission block, and copyright information}

%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as \texttt{acmart.pdf} document}

\newcommand{\tcpsnitch}{\texttt{TCPSnitch} }
\newcommand{\tcpsnitchns}{\texttt{TCPSnitch}}

\numberofauthors{1}
\author{
\alignauthor Gregory Vander Schueren\textsuperscript{1}, Quentin De Coninck\textsuperscript{2} and Olivier Bonaventure\textsuperscript{2} \\
    \affaddr{Universite Catholique de Louvain, Louvain-la-Neuve, Belgium}\\
    \email{\textsuperscript{1}gregory.vanderschueren@gmail.be, \textsuperscript{2}\{first.last\}@uclouvain.be}
}
\maketitle

\begin{abstract}
Networked applications interact with the TCP/IP stack through the socket API.
Over the years, the computing environment in which this API is being used has
dramatically changed and many extensions have been added. In this paper, we
propose and implement \tcpsnitchns, an open-source software that collects
detailed traces of the interactions between networked applications and the
TCP/IP stack and sends them to a publicly
available database, \tcpsnitchwebns, exposing various statistics. We collect
about 5~M API calls made by more than 130 Linux and Android applications on
24~K sockets. Our analysis reveals that the socket API usage in the wild
differs greatly from textbook usage. Many Internet sockets do not exchange
data, many API calls are redundant and many calls use tiny data buffers. On
Android, UDP sockets are mainly used as a shortcut to retrieve information
about the network configuration using \texttt{ioctl()} and most applications
use various socket options even if the Java API does not expose them directly.
\tcpsnitch and the associated dataset are publicly available.
\end{abstract}

\input{intro}
\input{methodology}
\input{dataset}
\input{udp}
\input{tcp}
\input{conclusion}
\newpage
\bibliographystyle{plain}
\bibliography{tcpsnitch}

\end{document}
